Job mobility and earnings growth: diffrerent markets, different outcomes.

### 2018-09-04 draft.Rmd
Update draft.Rmd

Countries differ in their rate of job mobility and turnover. Researchers often cite employment protection legislation when comparing such rates; however, the way mobility rewards workers may play a stronger role in determining mobility differences. We consider this idea through two aims. First we compare the effects of quits and promotions on earnings growth. Second, we consider their effects in two institutional settings (Germany and the UK). Studies exploring the effects of job mobility are rare, studies which compare and contrast their effects in separate institutional frameworks, or capitalisms, are rarer. We offer two findings. First, quits and promotions have significantly different effects on earnings growth, depsite both commonly labeled as "voluntary". Internal promotions yield significant earnings growth for workers in both countries. Quits have a minor effect, which is explained by a change in weekly working hours. Second, the effect of promotions is larger in Germany than in the UK. This suggests German workers see a greater premium for promotions than British workers. Workers are mobile in both countries, however, the high premium tied to internal mobility in Germany may act as an incentive to commit to the firm instead of the market. The article helps to understand country-differences in mobility rates, which go beyond explanations in a nationa's level of employment protection legislation.

@@

>>>>

Countries differ in their rate of job mobility and turnover. Researchers cite employment protection legislation as the key driver to such rates; however, the rewards or effects tied to mobility may play a stronger role in determining these differences. We consider this idea through two aims. First we compare the effects of quits and promotions on earnings growth. Second, we consider their effects in two institutional settings (Germany and the UK). Studies exploring the effects of job mobility are rare, studies which compare and contrast their effects in separate institutional frameworks, or capitalisms, are rarer. We offer two findings. First, quits and promotions have significantly different effects on earnings growth, depsite both commonly labeled as "voluntary". Internal promotions yield significant earnings growth for workers in both countries. Quits have a minor effect, which is explained by a change in weekly working hours. Second, the effect of promotions is larger in Germany than in the UK. This suggests the premium tied to promotion is greater in Germany than the UK. The high premium tied to internal mobility in Germany may act as an incentive to commit to the firm instead of the market, hence the lower rate of mobility among German workers. The article helps to understand country-differences in mobility rates; our explanations go beyond a nation's level of employment protection.

@@

Worker mobility is a key strategy in improving outcomes like wages and conditions. Routinely, authors show that workers stand to gain from mobility within and between firms. Despite this, capitalist countries differ in their rates of job mobility. This poses the question, are workers in less mobile countries starved for vacancies or opprtunities? We consider the impact mobility has on internal and external job mobility for the core workforce
